---
title: "Finding Pythagorean Triples by Brute Force Search"
author: "Your Name"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: false
    extra_dependencies: ["placeins"]
papersize: a4
fontsize: 11pt
geometry:
  - top=1in
  - bottom=1in
  - left=1.5in
  - right=1.5in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


# Empirical Results

The experimental results of your algorithm are plotted in Figure 1 and 2. The raw data is provided in Table \@ref(tab:data-summary) in the Appendix, along with the statistical fitting of the data to different growth models. 


```{r}
# Reading the data
data <- data.frame(read.table("NaivePythagoreanTripleFinder-stats.txt"));
names(data) <- c("maxval", "numtriples", "time")

# Power-law fit

n <- dim(data)[1];
max_x <- 10^(ceiling(log10(max(data$maxval))))
xx <- seq(min(data$maxval), max_x, by = 1)

b0 <- log(data$time[n]/data$time[n-1])/log(data$maxval[n]/data$maxval[n-1])
a0 <- data$time[n]/(data$maxval[n]^b0)
datafit_time <- nls(time ~ a * maxval^b, data=data, start = list(a = a0, b = b0))
fitfun_time <- function(x) predict(datafit_time, newdata=data.frame(maxval=x))

b0 <- log(data$numtriples[n]/data$numtriples[n-1])/log(data$maxval[n]/data$maxval[n-1])
a0 <- data$numtriples[n]/(data$maxval[n]^b0)
datafit_num <- nls(numtriples ~ a * maxval^b, data=data, start = list(a = a0, b = b0))
fitfun_num <- function(x) predict(datafit_num, newdata=data.frame(maxval=x))



pwrdata <- data.frame(
  "maxval" = xx,
  "ptime"  = fitfun_time(xx),
  "pnum"  = fitfun_num(xx)
)
  


```

```{r numtriples, fig.cap="Number of primitive Pythagorean triples up to a maximum value"}
# Graphical representation

library(ggplot2)
library(scales)
col <- c("data" = "blue", "power-law fit" = "red")
rx <-  seq(0, max_x, by = max_x/10)
figure <- ggplot(data=data, aes(x=maxval, y=numtriples)) + 
  geom_line(data = pwrdata, aes(x=maxval, y=pnum, colour = "power-law fit")) +
  geom_point(shape=21, size=3, aes(colour="data"),  fill="white") +
  scale_colour_manual(name = "", values = col, 
                      labels = c("data", 
                                   bquote(.(summary(datafit_num)$coefficients[1]) ~ n^.(summary(datafit_num)$coefficients[2])))
    ) +  
  guides(color = guide_legend(override.aes = list(shape = c(1, NA), 
                                                  linetype = c("blank", "solid")
                                                  ) 
                              )
         ) +
  scale_x_continuous (name = "maximum value", breaks = rx, 
                      labels = scales::number_format(accuracy = 1)) +
  scale_y_continuous(name = "#triples", labels = scales::number_format(accuracy = 1))+
  theme_bw() + 
  theme(legend.justification = c(0, 1), 
        legend.position = c(0, 1), 
        legend.box.margin=margin(c(5,5,5,5))) 

show(figure)
```


```{r time, fig.cap="Time required for finding primitive Pythagorean triples up to a maximum value"}
# Graphical representation

rx <-  seq(0, max_x, by = max_x/10)
figure <- ggplot(data=data, aes(x=maxval, y=time)) + 
  geom_line(data = pwrdata, aes(x=maxval, y=ptime, colour = "power-law fit")) +
  geom_point(shape=21, size=3, aes(colour="data"),  fill="white") +
  scale_colour_manual(name = "", values = col, 
                      labels = c("data", 
                                   bquote(.(summary(datafit_time)$coefficients[1]) ~ n^.(summary(datafit_time)$coefficients[2])))
    ) +
  guides(color = guide_legend(override.aes = list(shape = c(1, NA), 
                                                  linetype = c("blank", "solid")
                                                  ) 
                              )
         ) +
  scale_x_continuous (name = "maximum value", breaks = rx, 
                      labels = scales::number_format(accuracy = 1)) +
  scale_y_continuous(name = "time (s)", labels = scales::number_format(accuracy = 1))+
  theme_bw() + 
  theme(legend.justification = c(0, 1), 
        legend.position = c(0, 1), 
        legend.box.margin=margin(c(5,5,5,5))) 

show(figure)
```



# Discussion

Provide your interpretation of the results: 
(1) explain the meaning of each plot,
(2) discuss whether the results match the theoretical predictions of the problem, 
(3) discuss the complexity of your implementation.

\FloatBarrier

\setcounter{section}{0}
\renewcommand{\thesection}{\Alph{section}}

# Appendix

## Data Summary 

```{r data-summary}
library(knitr)

table_dataframe <- data.frame(
    "maxval" = data$maxval,
    "num" = data$numtriples,
    "time" = data$time
  )
kable(table_dataframe, "pipe",
      col.names = c("maxval", "#triples", "time"), 
      caption = "Summary of the experimental results")
```

## Model Fitting 
### Number of Pythagorean triples

```{r}
show(summary(datafit_num))
```

### Computational time

```{r}
show(summary(datafit_time))
```

  


